Patterns in Knowledge Production: Political Ruptures and Imperial Dynamics Shaping Public Discourse in Sweden and Finland, 1640–1828

### 2017-11-17 inst/examples/20170201-manuscript.Rmd
Fennica/Kungliga JM manuscript final Figures.

```{r init, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
# Default time span
min.year <- 1488
max.year <- 1828
library(ggthemes)
library(ggmap)
library(gisfin)
library(stringr)
library(dplyr)
library(tidyr)
library(reshape2)
library(ggplot2)
library(bibliographica)
library(fennica)
library(sorvi)
library(devtools)

@@

knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.path = "20170201_manuscript/", dpi = 300)
knitr::opts_chunk$set(dev = c("png", "jpeg", "cairo_ps"))
#knitr::opts_chunk$set(dev = "cairo_pdf") # Embed fonts
#knitr::opts_chunk$set(dev = "cairo_ps") # Embed fonts
knitr::opts_chunk$set(out.width = "17cm") # Default size 8.5cm ie 3.35 inch) per col
knitr::opts_chunk$set(out.format = "latex")

@@

```{r Figure_1, message=FALSE, warning=FALSE, fig.width=13, fig.height=5, echo=FALSE}

library(dplyr)
library(ggplot2)
# theme_set(theme_bw(20))
#theme_set(theme_linedraw(20))
theme_set(theme_light(20))

@@

print(p)

#postscript(file = "Figure_1.eps", width = 11, height = 5, paper = "special",
#              family = "sans", bg = "white")
#print(p)
#dev.off()
#library(extrafont)
#embed_fonts("Figure_1.eps", outfile="Figure_1.eps")
```

@@

```{r Figure_2, message=FALSE, warning=FALSE, fig.width=10, fig.height=4, echo=FALSE}
library(dplyr)
library(ggplot2)
theme_set(theme_bw(20))
df <- df0 %>% filter(publication_year >=1640 & publication_year <=1828) %>%
        group_by(catalog, publication_decade) %>% tally()

@@

```{r Figure_3prep, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=18, fig.height=5, fig.show="hide", results="hide"}
library(scales)
scientific_10 <- function(x) {
  parse(text=gsub("\\+", "", gsub("e", " %*% 10^", scientific_format()(x))))
}

@@

  p <- p + scale_fill_manual(values = c("darkgreen", "darkgray"))
  p <- p + scale_color_manual(values = c("darkgreen", "darkgray"))
  p <- p + xlab("Decade")
  p <- p + ylab("Paper (sheets)")
  p <- p + ylim(c(0, max(na.omit(df2$paper))))
  #p <- p + scale_shape_manual(values = factor(common.gatherings))
  #p <- p + scale_linetype_manual(values = factor(common.gatherings))

@@

library(cowplot)
# arrange the three plots in a single row
prow <- plot_grid(
           pics[[1]] + theme(legend.position="none"),
           pics[[2]] + theme(legend.position="none"),
           align = 'vh',
           labels = c("A", "B"),
           hjust = -1,
           nrow = 1
           )

@@

# add the legend underneath the row we made earlier. Give it 10% of the height
# of one plot (via rel_heights).
p <- plot_grid( prow, legend_b, ncol = 2, rel_widths = c(1, .2))
title <- ggdraw() + draw_label("Figure 3", fontface='bold')
```

```{r Figure_3, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=18, fig.height=5}
print(plot_grid(title, p, ncol=1, rel_heights=c(0.1, 1), hjust = 0))
```

@@

Loess smoothing.

```{r Figure_4, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=15, fig.show="last"}
cols <- list(Fennica = "blue", Kungliga = "darkred")
df <- df.full %>% filter(publication_year >= 1640 &
                         publication_year <= 1911) %>%
              group_by(catalog, publication_year) %>%
              summarize(title_length = median(title_length_wordcount),
	      		n = n())

@@

#pics[[unique(df$catalog)[[1]]]] <- pics[[unique(df$catalog)[[1]]]] + labs(title = "Figure 4")

library(cowplot)
# arrange the three plots in a single row
prow <- plot_grid(
           pics[[1]] + theme(legend.position="none"),
           pics[[2]] + theme(legend.position="none"),
           align = 'vh',
           labels = c("A", "B"),
           hjust = -1,
           nrow = 1
           )

@@

# add the legend underneath the row we made earlier. Give it 10% of the height
# of one plot (via rel_heights).
p <- plot_grid( prow, legend_b, ncol = 2, rel_widths = c(1, .2))
title <- ggdraw() + draw_label("Figure 4", fontface='bold')
p <- plot_grid(title, p, ncol=1, rel_heights=c(0.1, 1)) # rel_heights values control title margins
print(p)
```

@@

```{r Figure_5, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=15, fig.height=7}
pics <- list()
for (catalogue in na.omit(unique(df0$catalog))) {

@@

  theme_set(theme_bw(20))
  p <- ggplot(dff, aes(x = publication_decade, y = f)) +
     geom_bar(position = "stack", stat = "identity", color = "black",
       aes(fill = publication_place)) + 
     xlab("Decade") 
     #scale_fill_stata() 
     if (varname == "n") {
       p <- p + labs(subtitle = paste("Title count (", catalogue, ")", sep = ""), y = "Title count (%)")
     }
     if (varname == "paper") {
       p <- p + labs(subtitle = paste("Paper (", catalogue, ")", sep = ""), y = "Paper (%)")
     }
     if (varname == "publishers") {
       p <- p + labs(subtitle = paste("Publishers (", catalogue, ")", sep = ""), y = "Publishers (%)")
     }     
  p <- p + scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(dff$publication_decade)) + 50))
  p <- p + scale_fill_manual(values = city.colors[as.character(levels(dff$publication_place))])
  p <- p + guides(fill = guide_legend(title = ""))

@@

}
}
library(gridExtra)
#pics[[1]] <- pics[[1]] + # ggtitle("Figure 5") 
grid.arrange(pics[[1]], pics[[2]], pics[[4]], pics[[5]], top = "Figure 5", layout_matrix = matrix(c(1,2,3,4), nrow = 2, byrow=TRUE))
rm(pics)
```

@@

```{r Figure_6, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=4}
library(magrittr)
library(ggplot2)
library(dplyr)
v <- seq(1500, 1800, 100)
theme_set(theme_bw(20))
df <- df0 %>% filter(catalog == "Kungliga")

@@

p <- ggplot(df,
       aes(fill = period, y = paper.per.title, x = publication_place)) + 
       geom_bar(stat = "identity", color = "black", position = "dodge") +
       #scale_x_discrete(labels = c("1757-1765", "1766-1774", "1775-1783")) +
       #scale_fill_manual(values = c("darkgreen", "darkgray"))
       #scale_fill_brewer(palette="Greys") +
       scale_fill_stata() +
       #scale_fill_manual(values = city.colors[as.character(levels(df$publication_place))]) + 
       guides(fill = guide_legend(title = "Period")) +
       ylab("Paper (sheets)") + xlab("") 
       # ggtitle("Figure 6") 
       #ggtitl("Average paper consumption per title")

@@

```{r Figure_7, echo=FALSE, message=FALSE, warning=FALSE, fig.width=11, fig.height=4}

@@

  # Draw Figure
  theme_set(theme_bw(20))
  p <- ggplot() +
         geom_rect(data = rectangles, 
           aes(xmin=xmin, xmax=xmax,
	       ymin=ymin, ymax=ymax,
	       fill=shade), alpha=0.8) +
         scale_fill_manual(values = cols) +
	 guides(fill = "none")

@@

```{r Figure_8, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=12}
# Top publication places
library(bibliographica)

@@

theme_set(theme_bw(20))
brs <- seq(min(npub$publication_decade), max(npub$publication_decade), 10)  
p <- ggplot(npub, aes(x = publication_decade, y = n)) +
       geom_bar(stat = "identity", position = "stack", color = "black",
       		    aes(fill = publication_place)) + 
       xlab("Decade") +
       ylab("Publishers (n)") +
       #scale_fill_stata() +
       scale_fill_manual(values = city.colors[as.character(levels(npub$publication_place))]) +        
       guides(fill = guide_legend(reverse = FALSE, title = "")) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) 
       # ggtitle("Figure 8")
       #ggtitl(paste("Publishers (", catal, ")", sep = ""))

@@

```{r Figure_9, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=10}
library(dplyr)
catalogue <- "Fennica"
place <- "Vaasa"
minyear <- 1750
maxyear <- 1828

@@

```{r Figure_10, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=12}
library(dplyr)
place <- "Turku"
catalogue = "Fennica"
df = df0

@@

# TITLE COUNT
theme_set(theme_bw(20))
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
p <- ggplot(npub, aes(x = publication_decade, y = publisher)) +
      geom_point(aes(size = n)) +
      scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) + 
      xlab("Decade") +
      ylab("") +
      guides(size = guide_legend(title = "Title count (n)")) 
      # ggtitle("Figure 10")      
      #ggtitle(paste("Top publishers in ", place, " (", catalogue, ")", sep = ""))
      #ggtitle(paste("Figure 10: ", place, " (", catalogue, ")", sep = ""))

@@

```{r Figure_11, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
# Read historical population sizes
f <- system.file("extdata/population_sizes_in_cities.csv", package = "bibliographica")
pop <- read.csv(f)
pop <- melt(pop, "Year")
colnames(pop) <- c("publication_decade", "publication_place", "population")
pop <- as_data_frame(pop)
pop$publication_place <- as.character(pop$publication_place)

@@

```{r Figure_12, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
minyear <- 1640
maxyear <- 1828

@@

```{r Figure_13, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
# Take cities from Kungliga except Turku
cat <- "Kungliga"
df1 <- df0 %>% filter(publication_place %in% setdiff(cities, "Turku")) %>%
      	       filter(catalog == cat & gatherings == "8vo") %>%
	       group_by(publication_decade, publication_place) %>%
	       summarise(n = n(), paper = sum(paper, na.rm = TRUE))

@@

```{r Figure_14, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
# Take cities from Kungliga except Turku
df00 <- df.full %>% filter(publication_year >= 1640 & publication_year <= 1850)
df1 <- df00 %>% filter((publication_place %in% setdiff(cities, "Turku") & catalog == "Kungliga") |
                       (publication_place %in% "Turku" & catalog == "Fennica")) 
df1$publication_place[!df1$publication_place == "Stockholm"] <- "Other"
df1$publication_place <- droplevels(as.factor(as.character(df1$publication_place)))

@@

```{r Figure_15, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=7}
pics <- list()
theme_set(theme_bw(20))
myplaces <- c("Turku", "Greifswald", "Stockholm", "Uppsala", "Lund")
cnt <- 0
for (catalogue in c("Fennica", "Kungliga")) {

@@

grid.arrange(pics[[1]], pics[[8]], pics[[9]], pics[[10]], top = "Figure 15", layout_matrix = matrix(c(1,2,3,4), nrow = 2, byrow=TRUE))

rm(pics)
```

@@

```{r Figure_16, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5, fig.show="hold"}
catalogue <- "Fennica"
df <- filter(df0, catalog == "Fennica") %>%
  filter(publication_year >= 1640 & publication_year <= 1828) %>%
  select(publication_decade, language, subject_topic)
df <- unique(df)
df <- df %>% group_by(publication_decade, language) %>%
             summarise(n = length(unique(unlist(strsplit(subject_topic, ";")))))

@@

```{r Figure_17, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
sel <- c("hautajaiset", "häät", "juhlamenot")
catalogue <- "Fennica"
df <- df0
df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)

@@

```{r Figure_18, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5, fig.show="hold"}
sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat")
catalogue <- "Fennica"

@@

# PAPER CONSUMPTION
theme_set(theme_bw(20))
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_point(aes(shape = language, color = language), size = 5) +
       geom_line(aes(color = language), size = 1) +       
       xlab("Decade") +
       ylab("Paper (sheets)") +
       guides(shape = guide_legend(title = "Language"), color = guide_legend(title = "Language")) +
       #scale_color_stata() +
       #scale_color_manual(values = lang.colors[as.character(levels(df$language))]) +
       scale_color_manual(values = lang.colors[match(unique(df$language), names(lang.colors))]) +              
       # scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
       #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +       
       scale_y_continuous(label = scientific_10) 
       # ggtitle("Figure 18")       
       # ggtitle(paste("Devotional literature (", catalogue, ")", sep = ""))

>>>>

```{r init, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
# Checking figure dimensions
# identify -format "%[fx:w/300] by %[fx:h/300] inches\n" Figure_1-1.eps
# Checking resolution
# identify -verbose Figure_1-1.eps

# Default time span
min.year <- 1488
max.year <- 1828
library(ggthemes)
library(ggmap)
library(gisfin)
library(stringr)
library(dplyr)
library(tidyr)
library(reshape2)
library(ggplot2)
library(bibliographica)
library(fennica)
library(sorvi)
library(devtools)

@@

knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.path = "20170201_manuscript/", dpi = 300)
knitr::opts_chunk$set(dev = c("png", "jpeg", "cairo_ps"))
#knitr::opts_chunk$set(dev = "cairo_pdf") # Embed fonts
#knitr::opts_chunk$set(dev = "cairo_ps") # Embed fonts
knitr::opts_chunk$set(out.width = "17cm") # Default size 8.5cm ie 3.35 inch) per col
knitr::opts_chunk$set(out.format = "latex")
knitr::opts_chunk$set(fig.width=13.5,fig.height=8)

@@

```{r Figure_1, message=FALSE, warning=FALSE, echo=FALSE}

library(dplyr)
library(ggplot2)
# theme_set(theme_bw(20))
#theme_set(theme_linedraw(20))
theme_set(theme_light(25))

@@

@@

```{r Figure_2, message=FALSE, warning=FALSE, echo=FALSE}
library(dplyr)
library(ggplot2)
#theme_set(theme_bw(20))
df <- df0 %>% filter(publication_year >=1640 & publication_year <=1828) %>%
        group_by(catalog, publication_decade) %>% tally()

@@

```{r Figure_3prep, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.show="hide", results="hide", fig.width=27, fig.height=10}
library(scales)
scientific_10 <- function(x) {
  parse(text=gsub("\\+", "", gsub("e", " %*% 10^", scientific_format()(x))))
}

@@

  p <- p + scale_fill_manual(values = c("darkgreen", "darkgray"))
  p <- p + scale_color_manual(values = c("darkgreen", "darkgray"))
  p <- p + xlab("Decade")
  p <- p + ylab("Paper (sheets)")
  p <- p + ylim(c(0, max(na.omit(df2$paper))))

@@

library(cowplot)
# arrange the three plots in a single row
prow <- plot_grid(
           pics[[1]] + theme(legend.position="none"),
           pics[[2]] + theme(legend.position="none"),
           align = 'vh',
           labels = c("A", "B"),
	   label_size = 25,	   
           hjust = -1,
           nrow = 1
           )

@@

# add the legend underneath the row we made earlier. Give it 10% of the height
# of one plot (via rel_heights).
p <- plot_grid( prow, legend_b, ncol = 2, rel_widths = c(1, .1))
#title <- ggdraw() + draw_label("Figure 3", fontface='bold')
```

```{r Figure_3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=27, fig.height=10}
#print(plot_grid(title, p, ncol=2, rel_heights=c(0.1, 1), hjust = 0))
#print(p + theme_blank(30))
print(p)
```

@@

```{r Figure_4, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.show="last", fig.width=27, fig.height=10}
cols <- list(Fennica = "blue", Kungliga = "darkred")
df <- df.full %>% filter(publication_year >= 1640 &
                         publication_year <= 1911) %>%
              group_by(catalog, publication_year) %>%
              summarize(title_length = median(title_length_wordcount),
	      		n = n())

@@

library(cowplot)
prow <- plot_grid(
           pics[[1]] + theme(legend.position="none"),
           pics[[2]] + theme(legend.position="none"),
           align = 'vh',
           labels = c("A", "B"),
	   label_size = 25,
           hjust = -1,
           nrow = 1
           )

@@

# add the legend underneath the row we made earlier. Give it 10% of the height
# of one plot (via rel_heights).
p <- plot_grid( prow, legend_b, ncol = 2, rel_widths = c(.95, .08))
# title <- ggdraw() + draw_label("Figure 4", fontface='bold')
# p <- plot_grid(title, p, ncol=1, rel_heights=c(0.1, 1)) # rel_heights values control title margins
print(p)
```

@@

```{r Figure_5prep, echo=FALSE, message=FALSE, warning=FALSE, fig.width=27, fig.height=14, fig.show="none", results="hide"}
rm(p)
rm(prow)
rm(legend_b)
pics <- list()
for (catalogue in na.omit(unique(df0$catalog))) {

@@

  # theme_set(theme_bw(20))
  p <- ggplot(dff, aes(x = publication_decade, y = f)) +
     geom_bar(position = "stack", stat = "identity", color = "black",
       aes(fill = publication_place)) + 
     xlab("Decade") 
     #scale_fill_stata() 
     if (varname == "n") {
       p <- p + labs(subtitle = paste("Title count (", catalogue, ")", sep = ""), y = "Title count (%)")
     }
     if (varname == "paper") {
       p <- p + labs(subtitle = paste("Paper (", catalogue, ")", sep = ""), y = "Paper (%)")
     }
     if (varname == "publishers") {
       p <- p + labs(subtitle = paste("Publishers (", catalogue, ")", sep = ""), y = "Publishers (%)")
     }     
  p <- p + scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(dff$publication_decade)) + 50))
  p <- p + scale_fill_manual(values = city.colors[as.character(levels(dff$publication_place))])
  p <- p + guides(fill = guide_legend(title = ""))

@@

}
}
library(gridExtra)
#pics[[1]] <- pics[[1]] + # ggtitle("Figure 5") 
#grid.arrange(pics[[1]], pics[[2]], pics[[4]], pics[[5]], top = "Figure 5", layout_matrix = matrix(c(1,2,3,4), nrow = 2, byrow=TRUE))
#grid.arrange(pics[[1]], pics[[2]], pics[[4]], pics[[5]], layout_matrix = matrix(c(1,2,3,4), nrow = 2, byrow=TRUE))

library(cowplot)
# arrange the three plots in a single row
prow <- plot_grid(
           pics[[1]] + theme(legend.position="none"),
           pics[[2]] + theme(legend.position="none"),
           pics[[3]] + theme(legend.position="none"),
           pics[[4]] + theme(legend.position="none"),	   
           align = 'vh',
           # labels = c("A", "B", "", ""),
	   # label_size = 25,	   
           hjust = -1,
           nrow = 2
           )

legend_b <- get_legend(pics[[1]] + theme(legend.position="right"))

# Add the legend underneath the row we made earlier. Give it 10% of the height
# of one plot (via rel_heights).
p2 <- plot_grid( prow, legend_b, ncol = 2, rel_widths = c(1, .1))
```

```{r Figure_5, echo=FALSE, message=FALSE, warning=FALSE, fig.width=27, fig.height=14}
print(p2)
rm(pics)
```

@@

```{r Figure_6, echo=FALSE, message=FALSE, warning=FALSE}
library(magrittr)
library(ggplot2)
library(dplyr)
v <- seq(1500, 1800, 100)
# theme_set(theme_bw(20))
df <- df0 %>% filter(catalog == "Kungliga")

@@

p <- ggplot(df,
       aes(fill = period, y = paper.per.title, x = publication_place)) + 
       geom_bar(stat = "identity", color = "black", position = "dodge") +
       #scale_x_discrete(labels = c("1757-1765", "1766-1774", "1775-1783")) +
       #scale_fill_manual(values = c("darkgreen", "darkgray"))
       #scale_fill_brewer(palette="Greys") +
       scale_fill_stata() +
       #scale_fill_manual(values = city.colors[as.character(levels(df$publication_place))]) + 
       guides(fill = guide_legend(title = "Period")) +
       ylab("Paper per title (sheets)") + xlab("") 
       # ggtitle("Figure 6") 
       #ggtitl("Average paper consumption per title")

@@

```{r Figure_7, echo=FALSE, message=FALSE, warning=FALSE}

@@

  # Draw Figure
  # theme_set(theme_bw(20))
  p <- ggplot() +
         geom_rect(data = rectangles, 
           aes(xmin=xmin, xmax=xmax,
	       ymin=ymin, ymax=ymax,
	       fill=shade), alpha=0.8) +
         scale_fill_manual(values = cols) +
	 guides(fill = "none")

@@

```{r Figure_8, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
# Top publication places
library(bibliographica)

@@

#theme_set(theme_bw(20))
brs <- seq(min(npub$publication_decade), max(npub$publication_decade), 10)  
p <- ggplot(npub, aes(x = publication_decade, y = n)) +
       geom_bar(stat = "identity", position = "stack", color = "black",
       		    aes(fill = publication_place)) + 
       xlab("Decade") +
       ylab("Publishers (n)") +
       #scale_fill_stata() +
       scale_fill_manual(values = city.colors[as.character(levels(npub$publication_place))]) +        
       guides(fill = guide_legend(reverse = FALSE, title = "")) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) 
       # ggtitle("Figure 8")
       #ggtitl(paste("Publishers (", catal, ")", sep = ""))

@@

```{r Figure_9, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
library(dplyr)
catalogue <- "Fennica"
place <- "Vaasa"
minyear <- 1750
maxyear <- 1828

@@

```{r Figure_10, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
library(dplyr)
place <- "Turku"
catalogue = "Fennica"
df = df0

@@

# TITLE COUNT
#theme_set(theme_bw(20))
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
p <- ggplot(npub, aes(x = publication_decade, y = publisher)) +
      geom_point(aes(size = n)) +
      scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) + 
      xlab("Decade") +
      ylab("") +
      guides(size = guide_legend(title = "Title count (n)")) 
      # ggtitle("Figure 10")      
      #ggtitle(paste("Top publishers in ", place, " (", catalogue, ")", sep = ""))
      #ggtitle(paste("Figure 10: ", place, " (", catalogue, ")", sep = ""))

@@

```{r Figure_11, echo=FALSE, message=FALSE, warning=FALSE}
# Read historical population sizes
f <- system.file("extdata/population_sizes_in_cities.csv", package = "bibliographica")
pop <- read.csv(f)
pop <- melt(pop, "Year")
colnames(pop) <- c("publication_decade", "publication_place", "population")
pop <- as_data_frame(pop)
pop$publication_place <- as.character(pop$publication_place)

@@

```{r Figure_12, echo=FALSE, message=FALSE, warning=FALSE}
minyear <- 1640
maxyear <- 1828

@@

```{r Figure_13, echo=FALSE, message=FALSE, warning=FALSE}
# Take cities from Kungliga except Turku
cat <- "Kungliga"
df1 <- df0 %>% filter(publication_place %in% setdiff(cities, "Turku")) %>%
      	       filter(catalog == cat & gatherings == "8vo") %>%
	       group_by(publication_decade, publication_place) %>%
	       summarise(n = n(), paper = sum(paper, na.rm = TRUE))

@@

```{r Figure_14, echo=FALSE, message=FALSE, warning=FALSE}
# Take cities from Kungliga except Turku
df00 <- df.full %>% filter(publication_year >= 1640 & publication_year <= 1850)
df1 <- df00 %>% filter((publication_place %in% setdiff(cities, "Turku") & catalog == "Kungliga") |
                       (publication_place %in% "Turku" & catalog == "Fennica")) 
df1$publication_place[!df1$publication_place == "Stockholm"] <- "Other"
df1$publication_place <- droplevels(as.factor(as.character(df1$publication_place)))

@@

```{r Figure_15prep, echo=FALSE, message=FALSE, warning=FALSE, fig.width=27, fig.height=15, fig.show="hide", results="hide"}
pics <- list()
#theme_set(theme_bw(20))
myplaces <- c("Turku", "Greifswald", "Stockholm", "Uppsala", "Lund")
cnt <- 0
for (catalogue in c("Fennica", "Kungliga")) {

@@

#grid.arrange(pics[[1]], pics[[8]], pics[[9]], pics[[10]], top = "Figure 15", layout_matrix = matrix(c(1,2,3,4), nrow = 2, byrow=TRUE))
#grid.arrange(pics[[1]], pics[[8]], pics[[9]], pics[[10]], layout_matrix = matrix(c(1,2,3,4), nrow = 2, byrow=TRUE))

library(cowplot)
# arrange the three plots in a single row
prow <- plot_grid(
           pics[[1]] + theme(legend.position="none"),
           pics[[2]] + theme(legend.position="none"),
           pics[[3]] + theme(legend.position="none"),
           pics[[4]] + theme(legend.position="none"),	   
           align = 'vh',
           # labels = c("A", "B", "", ""),
	   # label_size = 25,	   
           hjust = -1,
           nrow = 2
           )

legend_b <- get_legend(pics[[1]] + theme(legend.position="right"))

# add the legend underneath the row we made earlier. Give it 10% of the height
# of one plot (via rel_heights).
p <- plot_grid( prow, legend_b, ncol = 2, rel_widths = c(1, .1))
rm(pics)
```

```{r Figure_15, echo=FALSE, message=FALSE, warning=FALSE, fig.width=27, fig.height=15}
print(p)
```

@@

```{r Figure_16, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold"}
catalogue <- "Fennica"
df <- filter(df0, catalog == "Fennica") %>%
  filter(publication_year >= 1640 & publication_year <= 1828) %>%
  select(publication_decade, language, subject_topic)
df <- unique(df)
df <- df %>% group_by(publication_decade, language) %>%
             summarise(n = length(unique(unlist(strsplit(subject_topic, ";")))))

@@

```{r Figure_17, echo=FALSE, message=FALSE, warning=FALSE}
sel <- c("hautajaiset", "häät", "juhlamenot")
catalogue <- "Fennica"
df <- df0
df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)

@@

```{r Figure_18, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold"}
sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat")
catalogue <- "Fennica"

@@

# PAPER CONSUMPTION
#theme_set(theme_bw(20))
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_point(aes(shape = language, color = language), size = 5) +
       geom_line(aes(color = language), size = 1) +       
       xlab("Decade") +
       ylab("Paper (sheets)") +
       guides(shape = guide_legend(title = "Language"), color = guide_legend(title = "Language")) +
       #scale_color_stata() +
       #scale_color_manual(values = lang.colors[as.character(levels(df$language))]) +
       scale_color_manual(values = lang.colors[match(unique(df$language), names(lang.colors))]) +              
       # scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
       #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +       
       scale_y_continuous(label = scientific_10) 
       # ggtitle("Figure 18")       
       # ggtitle(paste("Devotional literature (", catalogue, ")", sep = ""))

#print(p + theme_light(scalingfactor))
print(p)
```
